---
title: "Binomial Sampling"
author: "Cody Frisby"
date: "October 6, 2015"
output: 
  html_document: 
    keep_md: yes
---
Let's say the true proportion yield is 0.75. 
What's the sampling distribution for a yield such as this?
It will vary depending on the size of sample we take.
Here I'm simulating a sample of size 20 from a very large population
of 100000.  I'm taking 1000 samples from this population of size 20.
```{r}
x <- rbinom(100000,1,0.75)
xbar <- NULL
for (i in 1 : 1000) xbar <- c(xbar, mean(sample(x,20)))
mean(x)
mean(xbar)
quantile(xbar, c(0.025, 0.975))
```

Here's the distributions of the population and the means
```{r, echo=FALSE}
hist(x, col = "green")
hist(xbar, col="green")
```

But, what if we change some of the inputs.  Say, the number of samples gets smaller but the size of the samples gets larger.
```{r}
x <- rbinom(100000,1,0.75)
xbar <- NULL
for (i in 1 : 100) xbar <- c(xbar, mean(sample(x,50)))
mean(x)
mean(xbar)
quantile(xbar, c(0.025, 0.975))
```

```{r, echo=FALSE}
hist(xbar, col="green")
```
